`You Draw It': Implementation of visually fitted trends with \texttt{r2d3}

### 2022-11-14 2022-sdss-you-draw-it-manuscript.tex
submissions

\title{`You Draw It': Implementation of visually fitted trends with
\texttt{r2d3}}
\author{}
\date{}

\begin{document}
\maketitle
\begin{abstract}
How do statistical regression results compare to intuitive, visually
fitted results? Fitting lines by eye through a set of points has been
explored since the 20th century. Common methods of fitting trends by eye
involve maneuvering a string, black thread, or ruler until the fit is
suitable, then drawing the line through the set of points. In 2015, the
New York Times introduced an interactive feature, called `You Draw It,'
where readers are asked to input their own assumptions about various
metrics and compare how these assumptions relate to reality. This
research is intended to implement `You Draw It', adapted from the New
York Times, as a way to measure the patterns we see in data. In this
paper, we describe the adaptation of an old tool for graphical testing
and evaluation, eye-fitting, for use in modern web-applications suitable
for testing statistical graphics. We present an empirical evaluation of
this testing method for linear regression, and briefly discuss an
extension of this method to non-linear applications.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The `You Draw It' graphical task presented in this work is an example of
an interactive graphic. While any communication between user and device
can be considered an interaction, interactive graphics should be defined
as a user-driven direct manipulation of plots and plotting elements with
an immediate reaction (Unwin 1999, Becker et al.~1987, Eick \& Wills
1995). Here we discuss the use of `You Draw It' as a tool for
interactive reading, interactive testing, and interactive teaching as a
way to increase user experience and user engagement with data. The New
York Times first introduced the `You Draw It' feature as a tool for
interactive reading. The inclusion of interactive graphics in news and
media have been used to inform readers in efforts to reduce
misconceptions and aid in storytelling (Geidner et al. 2015;
George-Palilonis and Spillman 2011, 2013). In our work, we demonstrated
the use of the `You Draw It' method as a tool for interactive testing of
graphics. We collect data of the user drawn lines and compare to
statistical results in order to understand perceptual biases. While this
work has many possible directions for future work, there is a strong
application to extend the `You Draw It' tool for interactive teaching.
The line of best fit is introduced in secondary schools as a student's
first encounter with the concept of statistical association (Casey and
Nagle 2016). Casey (2015) and Casey (2016) conducted task based
interviews to examine student's conceptions of the line of best fit
prior to introducing the topic. The implications of using interactive
teaching tools for the line of best fit can help students make
connections between the shift in slope and the location of the best fit
line (Nagle, Casey, and Moore-Russo 2017). Casey and Wasserman (2015)
conducted similar task based interviews wish pre-service mathematics
teachers in order to understand the implications regarding teacher
preparation for the teaching of this topic. This demonstrates the use of
the `You Draw It' interactive tool for training purposes both within a
classroom setting and for those in the workforce.

>>>>

\title{`You Draw It': Implementation of visually fitted trends with
\texttt{r2d3}}
% \author{}
% \date{}

\begin{document}
\maketitle
\begin{abstract}
How do statistical regression results compare to intuitive, visually
fitted results? Fitting lines by eye through a set of points has been
explored since the 20th century. Common methods of fitting trends by eye
involve maneuvering a string, black thread, or ruler until the fit is
suitable, then drawing the line through the set of points. In 2015, the
New York Times introduced an interactive feature, called `You Draw It,'
where readers are asked to input their own assumptions about various
metrics and compare how these assumptions relate to reality. This
research is intended to implement `You Draw It', adapted from the New
York Times, as a way to measure the patterns we see in data. In this
paper, we describe the adaptation of an old tool for graphical testing
and evaluation, eye-fitting, for use in modern web-applications suitable
for testing statistical graphics. We present an empirical evaluation of
this testing method for linear regression, and briefly discuss an
extension of this method to non-linear applications.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

The `You Draw It' graphical task presented in this work is an example of
an interactive graphic. Here we discuss the use of `You Draw It' as a
tool for interactive reading, interactive testing, and interactive
teaching as a way to increase user experience and user engagement with
data. The New York Times first introduced the `You Draw It' feature as a
tool for interactive reading. The inclusion of interactive graphics in
news and media have been used to inform readers in efforts to reduce
misconceptions and aid in storytelling (Geidner et al. 2015;
George-Palilonis and Spillman 2011, 2013). In our work, we demonstrated
the use of the `You Draw It' method as a tool for interactive testing of
graphics. We collected and compared data from user drawn lines to
statistical results in order to understand perceptual biases. While this
work has many possible directions for future work, there is a strong
application to extend the `You Draw It' tool for interactive teaching.
The line of best fit is introduced in secondary schools as a student's
first encounter with the concept of statistical association between
multiple variables (Casey and Nagle 2016). Casey (2015) and Casey (2016)
conducted task based interviews to examine student's conceptions of the
line of best fit prior to introducing the topic. The implications of
using interactive teaching tools for the line of best fit can help
students make connections between the shift in slope and the location of
the best fit line (Nagle, Casey, and Moore-Russo 2017). Casey and
Wasserman (2015) conducted similar task based interviews with
pre-service mathematics teachers in order to understand the effects
regarding teacher preparation for the teaching of this topic. This
demonstrates the use of the `You Draw It' interactive tool for training
purposes both within a classroom setting and for those in the workforce.
